Jeff Goldsmith

### 2018-06-02 papers.Rmd
fixing links; level up
updating papers list

## 2017
D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2017+).
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> 
accepted.
[[PDF](Downloads/HetFCPA.pdf)]

M. S. Maurer, E. Horn, A. Reyentovich, V. V. Dickson, S. Pinney, D. Goldwater, N. E. Goldstein, O. Jimenez, S. Teruya, **J. Goldsmith**, S. Helmke, M. Yuzefpolskaya, and G. R Reeves (2017+).
Can a Left Ventricular Assist Devices in Advanced Systolic Heart Failure Improve or Reverse the Frailty Phenotype?
<i> Journal of the American Geriatrics Society, </i> accepted.

K. M. Diaz, D. J. Krupka, M. J. Chang, I. M. Kronish, N. Moise, **J. Goldsmith**, and J. E. Schwartz (2017+).
Wrist-based cut-points for moderate- and vigorous-intensity physical activity for the Actical accelerometer in adults.
<i> Journal of Sports Sciences, </i>
accepted.

J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017+).
A short and distinct time window for recovery of arm motor control after stroke revealed with a global measure of trajectory kinematics.
<i> Neurorehabilitation and Neural Repair, </i>
accepted.

M. Kronish, K. M. Diaz, **J. Goldsmith**, N. Moise, and J. E. Schwartz.
Objectively measured adherence to physical activity guidelines after acute coronary syndrome (2017+).
<i> Journal of the American College of Cardiology, </i>
accepted.

**J. Goldsmith** and J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017+).
<i> Statistics in Medicine, </i>
accepted.
[[PDF](Downloads/VBVS.pdf)
| [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
Habitual selection of reaction times.
<i> eLife, </i> 
<b>6</b> e28075.
[[Link](https://elifesciences.org/articles/28075)]

@@

A. L. Wong, **J. Goldsmith**, J Krakauer (2016).
A motor planning stage represents the shape of upcoming movement trajectories.
<i> Journal of Neurophysiolog, </i>
<b>116</b> 296-305.
[[Link](http://jn.physiology.org/content/116/2/296)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27098032)]

>>>>

## 2018

D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018+).
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> 
accepted.
[[PDF](Downloads/HetFCPA.pdf)]

H. Rosenblum, A. Castano, J. Alvarez, **J. Goldsmith**, S. Helmke, M.S. Maurer (2018).
TTR (Transthyretin) Stabilizers Are Associated With Improved Survival in Patients With TTR Cardiac Amyloidosis.
<i> Circulation: Heart Failure, </i>
<b>11</b> e004769.
[[Link](http://circheartfailure.ahajournals.org/content/11/4/e004769)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/29615436)]

K. M. Diaz, D. J. Krupka, M. J. Chang, I. M. Kronish, N. Moise, **J. Goldsmith**, and J. E. Schwartz (2018).
Wrist-based cut-points for moderate- and vigorous-intensity physical activity for the Actical accelerometer in adults.
<i> Journal of Sports Sciences, </i>
<b>36</b> 206-212.
[[Link](https://shapeamerica.tandfonline.com/doi/abs/10.1080/02640414.2017.1293279)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28282744)]

## 2017

K. M. Diaz, **J. Goldsmith**, H. Greenlee, G. Strizich, Q. Qi, Y. Mossavar-Rahmani, D. C. Vidot, C. Buelna, C. E. Brintz, T. Elfassy, L. C. Gallo, M. L. Daviglus, D. Sotres-Alvarez, R. C. Kaplan (2017).
Prolonged, Uninterrupted Sedentary Behavior and Glycemic Biomarkers Among US Hispanic/Latino Adults
<i> Circulation, </i> 
<b>136</b> 1362-1373.
[[Link](http://circ.ahajournals.org/content/136/15/1362)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28835368)]

M. S. Maurer, E. Horn, A. Reyentovich, V. V. Dickson, S. Pinney, D. Goldwater, N. E. Goldstein, O. Jimenez, S. Teruya, **J. Goldsmith**, S. Helmke, M. Yuzefpolskaya, and G. R Reeves (2017).
Can a Left Ventricular Assist Devices in Advanced Systolic Heart Failure Improve or Reverse the Frailty Phenotype?
<i> Journal of the American Geriatrics Society, </i> 
<b>65</b> 2383-2390.
[[Link](https://onlinelibrary.wiley.com/doi/full/10.1111/jgs.15124)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28940248)]

J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017).
A short and distinct time window for recovery of arm motor control after stroke revealed with a global measure of trajectory kinematics.
<i> Neurorehabilitation and Neural Repair, </i>
<b>31</b> 552-560.
[[Link](http://journals.sagepub.com/doi/abs/10.1177/1545968317697034)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28506149)]

M. Kronish, K. M. Diaz, **J. Goldsmith**, N. Moise, and J. E. Schwartz.
Objectively measured adherence to physical activity guidelines after acute coronary syndrome (2017).
<i> Journal of the American College of Cardiology, </i>
<b>69</b> 1205.
[[Link](https://www.sciencedirect.com/science/article/pii/S0735109717300372?via%3Dihub)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28254185)]

**J. Goldsmith** and J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017).
<i> Statistics in Medicine, </i>
<b>36</b> 2237-2250.
[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sim.7254/full)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28211085)
| [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017).
Habitual selection of reaction times.
<i> eLife, </i> 
<b>6</b> e28075.
[[Link](https://elifesciences.org/articles/28075)]

@@

A. L. Wong, **J. Goldsmith**, J Krakauer (2016).
A motor planning stage represents the shape of upcoming movement trajectories.
<i> Journal of Neurophysiology, </i>
<b>116</b> 296-305.
[[Link](http://jn.physiology.org/content/116/2/296)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27098032)]
